Deciphering Mortality in Alberta: A Multifaceted Analysis

### 2024-03-16 outputs/paper/paper.qmd
final draft for scripts

>>>>

## Possible Improvements

While our study sheds light on Alberta's mortality trends, it's important to recognize its limitations. Our analysis depends on available data, which might not capture every detail affecting mortality rates. The methods we used, although useful for spotting general trends, might oversimplify the complex factors at play, including how policies or environmental changes impact health. Future research should aim to use more detailed data and explore these complexities more deeply. It's also essential to look at the long-term effects of changes in public health policies and the environment. By digging deeper into these areas and using a mix of quantitative and qualitative research, we can better understand and address the factors that influence health outcomes in Alberta.
